\documentclass[letterpaper,10pt]{article}
% Essential packages only
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\setlength{\footskip}{3.60004pt}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{soul}
\usepackage[margin=0.5in]{geometry}
\usepackage[default]{sourcesanspro}

% Page style
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% General formatting
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

% Highlight color
\definecolor{lightyellow}{cmyk}{0.00, 0.05, 0.20, 0.00}
\sethlcolor{lightyellow}

%--------------- Custom commands -----------------------
\newcommand{\sectionspace}{\vspace{-20pt}}
\newcommand{\subheadingtitlevspace}{\vspace{-3pt}}
\newcommand{\resumeItem}[1]{\item{#1 \vspace{-4pt}}}
\newcommand{\titleItem}[1]{\textbf{#1}}
\newcommand{\highlight}[1]{\textsl{\textbf{#1}}}
\newcommand{\resumeSubheading}[4]{
  \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}l@{}l}     
      {#1} & \titleItem{#3} | {#2} & \textit{#4}\\
    \end{tabular*}\vspace{-10pt}
}
\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{#1} & \textit{#2} \\
    \end{tabular*}\vspace{-2pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        #1 & \textit{ #2} \\
    \end{tabular*}\vspace{-9pt}
}
\newcommand{\resumeSubHeadingListStart}{\subheadingtitlevspace\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-8pt}}

%-------------------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%-------------------------------------------------------

\begin{document}

% ----------HEADING---------------------
\begin{flushleft}
    \textbf{\huge Bernard Birendra Das} \\
    \textit{Kolkata, West Bengal} $|$
    \textit{(+91) 798-000-3127} $|$
    \href{https://berniespace.dev}{{\textit{@website}}} $|$
    \href{mailto:bernardbdas@gmail.com}{{\textit{@mail}}} $|$
    \href{https://linkedin.com/in/bernardbdas}{{\textit{@linkedin}}} $|$
    \href{https://github.com/bernardbdas}{{\textit{@github}}}
    \vspace{-8pt}
\end{flushleft}

% ---------- PROFESSIONAL SUMMARY ------
\section{Professional Summary}
\vspace{-3pt}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item{Versatile developer with a Master's in Computer Science, distinguished for collaborative skills and a track record of independently delivering impactful results. Ample experience in full-stack development, delivering well-documented, tested, and operable code. Efficient in collaborating and communicating new ideas and opinions.}
\end{itemize}
\sectionspace

% ---------- AWARDS AND CERTIFICATIONS ------
\section{Awards and Certifications}
    \resumeSubHeadingListStart
        \resumeProjectHeading{\href{https://www.freecodecamp.org/certification/bernardbdas/foundational-c-sharp-with-microsoft}{\titleItem{Foundational C\# with Microsoft Developer Certification}}}{September 2023}
        \resumeProjectHeading{\href{https://www.credly.com/badges/bdf2f146-b8c1-4cc0-b3df-81980f4df784}{\titleItem{AWS Academy Graduate - AWS Academy Cloud Foundations}}}{November 2022}
    \resumeSubHeadingListEnd

% ---------- TECHNICAL SKILLS ------------
\section{Technical Skills}
\subheadingtitlevspace
\begin{itemize}[leftmargin=0.15in, label={}]
    \item{\titleItem{Languages}{: JavaScript, LaTeX, Python, Java, C\#, C/C++, SQL (Postgres, MS-SQL, MySQL)} \\
    \titleItem{Frameworks}{: MERN, MEAN, MEVN, Svelte, Remix, SolidJS, Django, Flask, React Native} \\
    \titleItem{DevOps and API Tools}{: Git, Docker, OpenShift, Kubernetes, Azure DevOps, Swagger, Postman} \\
    \titleItem{Data Analytics Tools}{: PowerBI, R, TensorFlow, PyTorch, Pandas, Polars, Numpy, Scikit-learn, Prophet, Matplotlib, Seaborn, Plotly, MLFlow, Apache Airflow} \\
    \titleItem{Machine Learning Tools}{: TensorFlow, PyTorch, Scikit-learn, Prophet, ARIMA/SARIMA, MLFlow, Apache Airflow, Apache Spark, Dask, Kubeflow, Google Cloud AI} \\
    \titleItem{Others}{: Data Modeling, Agile (Scrum/Kanban), SOLID, Design Patterns,  Debugging, Root Cause Analysis}}
\end{itemize}
\sectionspace

% ---------- EXPERIENCE ------------------
\section{Experience}

\resumeSubHeadingListStart
\resumeProjectHeading{\titleItem{Software Developer} $|$ \emph{Simplify3x Software Private Limited} $|$ \textbf{2 yrs 5 mos}}{January 2023 -- May 2025} 
    \resumeItemListStart
        \resumeItem{Worked on the core product team of SimplifyQA product as a feature owner for PDF Reports and Pipeline Executions modules.}
        \resumeItem{Designed and implemented RESTful APIs and microservices in Node.js, significantly reducing service response times and improving overall system scalability.}
        \resumeItem{Developed dynamic, data-driven dashboards using Angular and D3.js, enabling real‑time visualization of key performance metrics for business stakeholders.}
        \resumeItem{Collaborated with product owners, QA engineers, and DevOps to establish a CI/CD pipeline on Azure DevOps, cutting deployment times from hours to minutes.}
        \resumeItem{Mentored two junior developers through code reviews and pair‑programming sessions, fostering best practices and accelerating feature delivery.}
    \resumeItemListEnd
\resumeSubHeadingListEnd


% ---------- EDUCATION -------------------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading{CHRIST (Deemed to be University), Bangalore}{CGPA : --}{PhD in Data Science}{December 2024 -- present}
    \resumeSubheading{CHRIST (Deemed to be University), Bangalore}{CGPA : 8.66}{Master of Computer Applications (MCA)}{June 2021 -- June 2023}
    \resumeSubheading{St. Xavier's College (Autonomous), Kolkata}{CGPA : 7.20}{Bachelor of Computer Science Honours}{June 2018 -- June 2021}
    % \resumeSubheading{Auxilium Convent School, Barasat}{CGPA : 7.12}{ISC}{June 2016 -- June 2018} 
    % \resumeSubheading{Auxilium Convent School, Barasat}{CGPA : 7.64}{ICSE}{June 2004 -- June 2016}
\resumeSubHeadingListEnd
\vspace{-8pt}

% ---------- PROJECTS --------------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading{\titleItem{Project 1} $|$ \emph{Django, IBM Cloud, SQLite, Function-as-a-Service, Kubernetes, OpenShift}}{Nov 2023}
      \resumeItemListStart
        \resumeItem{In cursus turpis massa tincidunt dui. Cras pulvinar mattis nunc sed blandit libero volutpat sed. Suspendisse potenti nullam ac tortor.}
        \resumeItem{Ut consequat semper viverra nam libero justo laoreet sit amet. Feugiat nisl pretium fusce id velit ut tortor pretium.}
      \resumeItemListEnd
    \resumeProjectHeading{\titleItem{Project 2} $|$ \emph{Python, numpy. D3.js}}{Spring 2022}
      \resumeItemListStart
        \resumeItem{Ut consequat semper viverra nam libero justo laoreet sit amet. Feugiat nisl pretium fusce id velit ut tortor pretium.}
        \resumeItem{In cursus turpis massa tincidunt dui. Cras pulvinar mattis nunc sed blandit libero volutpat sed. Suspendisse potenti nullam ac tortor.}
      \resumeItemListEnd
    \resumeProjectHeading{\titleItem{Project 3} $|$ \emph{\LaTeX}}{November 2021}
      \resumeItemListStart
        \resumeItem{In cursus turpis massa tincidunt dui. Cras pulvinar mattis nunc sed blandit libero volutpat sed. Suspendisse potenti nullam ac tortor.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\end{document}
