%-------------------------
% Resume in Latex
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage{ifsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{xcolor}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\usepackage{tabularx}
% fontawesome
\usepackage{fontawesome5}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}
\newcommand{\resumeItemNonBold}[2]{
  \item\small{
    {#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemHead}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\resumeSubItemNoBold}[2]{\resumeItemNonBold{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{center}
    \textbf{\Large\scshape GYAN DEV MISHRA} \\ \vspace{1pt}
    \small \faPhone* 8956886326 $|$ \faEnvelope \hspace{2pt} \href{mailto:dishantsharma44.ds@gmail.com}
   {\color{black} \underline {gyan9427@gmail.com}} $|$ 
    \faLinkedin \hspace{2pt}\href{www.linkedin.com/in/gyan-dev-mishra-718398145} {\color{black} \underline{gyan-dev-mishra}}$|$\address{ \textifsymbol{18} Bengaluru,Karnataka}\\
\end{center}
\vspace{-15pt}
%-----------EDUCATION-----------------
% --------PROGRAMMING SKILLS------------
\section{Skills}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
    
     \textbf{Languages} {: Python, Php, SQL, Javascript.}\vspace{2pt} \\
     \textbf{Tools}     {: GitHub, Jupyter-Notebook}\\

      \textbf{Web development}     {: HTML, CSS, JavaScript, React, NodeJS, D3-JS}\\
     
     \textbf{Frontend \& Backend}     {: Node.js, React, Restful APIs, PostgreSQL, MySQL, Github} \\
\end{itemize} 


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Simplify3x Pvt Ltd.}{Bengaluru,India}
    {Software Development Engineer }{May 2022- Present}
    
        \resumeItemListStart
        \vspace{-2pt}
            \resumeItemHead{}{Developed and maintained web applications using NodeJS, React and Python.} 
            \resumeItemHead{}{Worked heavily on data visualization with D3JS.} 
            \resumeItemHead{}{Working on Python scripts to automate Rest APIs deployment and for generating authentication tokens.}
            \resumeItemHead{}{Designed and implemented RESTful APIs for seamless integration of the applications.}
        \resumeItemListEnd
        
    \resumeSubheading
    {KADAMTECH Pvt Ltd.}{Jaipur,Rajasthan,India}
    {Web Developer }{ August 2021 - April 2022}
    
        \resumeItemListStart
        \vspace{-2pt}
            \resumeItemHead{}{Worked as full-stack developer and dealt with technologies like LARAVEL, Nodejs, React. } 
            \resumeItemHead {}{Provided services to IndiaMART and Developed interfaces for the GLAdmin team, for customer usage.}
            \resumeItemHead {}{worked for UI-Transformation of existing web page with React Js, material}
            \resumeItemHead {}{worked for Enek-Luso, A React js based E-commerce project for Eye-wears. }
        \resumeItemListEnd  

    \resumeSubheading
    {Qntalion}{Jaipur,Rajasthan,India}
    {Software Development Engineer }{ February 2020 - September 2021}
    
        \resumeItemListStart
        \vspace{-2pt}
            \resumeItemHead{}{Developed and maintained web applications using PHP, Python, React Js. } 
            \resumeItemHead {}{Designed and implemented RESTful APIs for seamless integration of the applications.}
            \resumeItemHead {}{Majorly worked as Frontend developer, while working a lot on CSS.}
            \resumeItemHead {}{carousel development, beautiful card designs and shadow effects. }
        \resumeItemListEnd  

     \resumeSubheading
    {Freelance Developer}{Pune,Maharashtra,India}
    { }{ December 2018 - August 2019}
    
        \resumeItemListStart
        \vspace{-2pt}
            \resumeItemHead{}{Developed and maintained web applications using PHP, Python Javascript, CSS, for Business owners and other developers. } 
        \resumeItemListEnd  

     \resumeSubheading
    {Physics Teacher}{Jaipur,Rajasthan,India}
    {Sr. Secondary }{ Prior to 2018}
    
        \resumeItemListStart
        \vspace{-2pt}
            \resumeItemHead{}{Trained students for IIT, NEET, 12th boards Physics } 
        \resumeItemListEnd  
    
    \resumeSubHeadingListEnd

    
        
    
% \vspace{-0.15in}

%----------- PROJECTS-----------------
\section {\href{https://github.com/Dishant-Sharma/Data_Science_Projects} {\color{black} \underline{Personal Projects}}}
  \resumeSubHeadingListStart
  \resumeItem 
    {\href{https://github.com/gyan9427/blockchain-js}{\color{black} {Block-chain Development:}}}{Developed a fully functional blockchain backend using Node.js. } 
  \resumeItem 
    {{\color{black} {E-commerce Website}}}
    {Developed a fully functional e-commerce website using React, Node.js, and MySQL. Implemented features such as product search, shopping cart, and secure checkout.} 
    \resumeItem 
    {{\color{black} {Inventory Management System}}}
    {Designed and implemented an inventory management system for a retail store using Java and MySQL. Implemented features such as real-time inventory tracking, product ordering, and sales reporting.} 
    \resumeItem 
    {{\color{black} {ETL Data Pipeline using Python}}}
    {Created an ETL pipeline which extracts data from one S3 bucket and transfers to other with some minor data manipulations.}
    \resumeItem 
    {{\color{black} {Neural Networks for Deep Learning from scratch}}}
    {Created a neural network Library including all the mathematical functionalities in Javascript}
  \resumeSubHeadingListEnd
  \vspace{-11pt}


%-----------PUBLICATIONS-----------------

  \section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bachelor of Technology, CIITM, Jaipur}{2007 - 2011}
      {Instrumentation}{45 percent}
      \vspace{-5pt}
    
    \resumeSubheading
      {{\color{black} Sr. Secondary, Tagore Public School, Jaipur}}{2006 - 2007}
      {}{PCM 70 percent}
     
    \resumeSubheading
      {Higher Secondary, Tagore Public School, Jaipur}{2004 - 2006}
      {}{65 percent}
      \vspace{-5pt}
    
%    \resumeSubheading
%      {Ramjas Public School (Day Boarding)}{Year of Passing: 2015}
%      {CBSE Board: 12\textsuperscript{th} (Senior Secondary Examination) }{\%age: 74.6}
%      \vspace{-5pt}
    
 %   \resumeSubheading
%      {Ramjas Public School (Day Boarding)}{Year of Passing: 2012}
%      {CBSE Board: 10\textsuperscript{th} (Secondary Examination) }{CGPA: 7.8}
    
  \resumeSubHeadingListEnd
  \vspace{-13pt}



%-----------Declaration------
%\section{Declaration}
%\begin{itemize}[leftmargin=0in, label={}]
% \small{\item{
% {I hereby declare that all the information reflected %above is true to the best of my belief.}\vspace{1pt}\\
% \hspace{360pt}{-Dishant Sharma}{} \\
% }}
% \end{itemize} 

%-------------------------------------------
\end{document}

