\documentclass{bernard-resume-ats}

%-------------------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
%-------------------------------------------------------

\begin{document}

% ----------HEADING---------------------
\begin{flushleft}
    \textbf{\huge Bernard Birendra Das} \\
    \textit{Software Developer} $|$
    \textit{Kolkata, West Bengal} $|$
    \textit{(+91) 798-000-3127} $|$
    % \href{https://berniespace.dev}{{\textit{@website}}} $|$
    \href{mailto:bernardbdas@gmail.com}{{\textit{@mail}}} $|$
    \href{https://linkedin.com/in/bernardbdas}{{\textit{@linkedin}}} $|$
    \href{https://github.com/bernardbdas}{{\textit{@github}}}
    \vspace{-8pt}
\end{flushleft}

% ---------- PROFESSIONAL SUMMARY ------
\section{Professional Summary}
\vspace{-3pt}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item{Results-driven software developer with a strong foundation in data science, full stack web development, and DevOps. Experienced in designing and deploying scalable, production-grade solutions using modern frameworks, cloud platforms, and MLOps/DevOps best practices. Adept at collaborating in cross-functional teams, leading feature delivery, and mentoring junior engineers. Passionate about building impactful products, automating workflows, and driving continuous improvement in fast-paced environments.}
\end{itemize}
\sectionspace

% ---------- AWARDS AND CERTIFICATIONS ------
\section{Awards and Certifications}
    \resumeSubHeadingListStart
        \resumeProjectHeading{\href{https://www.freecodecamp.org/certification/bernardbdas/foundational-c-sharp-with-microsoft}{\titleItem{Foundational C\# with Microsoft Developer Certification}}}{September 2023}
        \resumeProjectHeading{\href{https://www.credly.com/badges/bdf2f146-b8c1-4cc0-b3df-81980f4df784}{\titleItem{AWS Academy Graduate - AWS Academy Cloud Foundations}}}{November 2022}
    \resumeSubHeadingListEnd

% ---------- TECHNICAL SKILLS ------------

\subfile{sections/skills/data-science-skills.tex}
% \subfile{sections/skills/fullstack-webdev-skills.tex}
% \subfile{sections/skills/devops-skills.tex}

% ---------- EXPERIENCE ------------------
\section{Experience}

\resumeSubHeadingListStart
\resumeProjectHeading{\titleItem{Software Developer} $|$ \emph{Simplify3x Software Private Limited} $|$ \textbf{2 yrs 5 mos}}{January 2023 -- May 2025} 
    \resumeItemListStart
        \resumeItem{Worked on the core product team of SimplifyQA product as a feature owner for PDF Reports and Pipeline Executions modules.}
        \resumeItem{Designed and implemented RESTful APIs and microservices in Node.js, significantly reducing service response times and improving overall system scalability.}
        \resumeItem{Developed dynamic, data-driven dashboards using Angular and D3.js, enabling real‑time visualization of key performance metrics for business stakeholders.}
        \resumeItem{Collaborated with product owners, QA engineers, and DevOps to establish a CI/CD pipeline on Azure DevOps, cutting deployment times from hours to minutes.}
        \resumeItem{Mentored two junior developers through code reviews and pair‑programming sessions, fostering best practices and accelerating feature delivery.}
    \resumeItemListEnd
\resumeSubHeadingListEnd


% ---------- EDUCATION -------------------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading{CHRIST (Deemed to be University), Bangalore}{CGPA : N/A}{PhD in Data Science}{December 2024 -- present}
    \vspace{0.5em}
    \resumeSubheading{CHRIST (Deemed to be University), Bangalore}{CGPA : 8.66}{Master of Computer Applications (MCA)}{June 2021 -- June 2023}
    \vspace{0.5em}
    \resumeSubheading{St. Xavier's College (Autonomous), Kolkata}{CGPA : 7.20}{Bachelor of Computer Science Honours}{June 2018 -- June 2021}
    \vspace{0.5em}
    \resumeSubheading{Auxilium Convent School, Barasat}{CGPA : 7.12}{12th Grade, ISC Board}{June 2016 -- June 2018} 
    \vspace{0.5em}
    \resumeSubheading{Auxilium Convent School, Barasat}{CGPA : 7.64}{10th Grade, ICSE Board}{June 2004 -- June 2016}
\resumeSubHeadingListEnd
\vspace{-8pt}

% ---------- PROJECTS --------------------
\newpage
\subfile{sections/projects/data-science-projects.tex}
% \subfile{sections/projects/fullstack-webdev-projects.tex}
% \subfile{sections/projects/devops-projects.tex}

\end{document}
