%-------------------------
% Resume in Latex
%------------------------

\documentclass[letterpaper, 10pt]{article}

\usepackage{latexsym}
\usepackage{ifsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{xcolor}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\usepackage{tabularx}

% fontawesome
\usepackage{fontawesome5}
\input{glyphtounicode}
\pagestyle{fancy}
\fancyhf{}              % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]
    {\item\small
        {\textbf{#1}
        { #2 \vspace{-2pt}}
    }
}

\newcommand{\resumeItemNonBold}[2]
    {\item\small
        {{#1}{ #2 \vspace{-2pt}}
    }
}

\newcommand{\resumeItemHead}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\resumeSubItemNoBold}[2]{\resumeItemNonBold{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{center}
    \textbf{\Large\scshape BERNARD BIRENDRA DAS} \\ \vspace{2pt}
    \small \faPhone* 7980003127 $|$ 
    \faEnvelope \hspace{2pt} \href{mailto:bernardbdas@gmail.com}{\color{black} \underline {bernardbdas@gmail.com}} $|$ 
    \faLinkedin \hspace{2pt}\href{www.linkedin.com/in/bernardbdas/} {\color{black} \underline{bernardbdas}} \hspace{1pt} $|$ 
    \address{ \textifsymbol{18} Kolkata, West Bengal}\\
\end{center}
\vspace{-15pt}

% --------PROGRAMMING SKILLS------------
\section{SKILLS}
\begin{itemize}[leftmargin=0in, label={}]
\vspace{2pt}
    \small{
    \item {
        \textbf{Languages} {: Python, JAVA, R, SQL, Hive.} \vspace{2pt} \\}
    \item {
        \textbf{Tools} {: Git, Jenkins, Power Bi, Tableau, Streamlit, MongoDB, Oracle 11g, Apache Hadoop.}\vspace{2pt} \\}
    \item {
        \textbf{Frameworks Known} {: TensorFlow, PyTorch, Hadoop.}\vspace{2pt} \\}
    }
\end{itemize} 

%-----------EXPERIENCE-----------------
\section{EXPERIENCE}
    \resumeSubheading
    {Simplify3x Pvt. Ltd.}{Bengaluru, India}
    {Software Engineer}{June 2023 - Present}
        \resumeItemListStart
            \resumeItemHead{}{Worked on MEAN Stack for front-end and back-end development.}
            \resumeItemHead{}{Worked on a project for OCR model-based web driver implementation.}
            \resumeItemHead{}{Developed a Semantic Search Engine library in Python.}
            \resumeItemHead{}{Created interactive PowerBI dashboards for client meetings.}
        \resumeItemListEnd
    \resumeSubheading
    {}{}
    {Software Engineer Intern}{January 2023 - May 2023}
        \resumeItemListStart
            \resumeItemHead{}{Proficient in Selenium automation testing using Java and Python, with expertise in TestNG and JUnit frameworks.} 
            \resumeItemHead{}{Successfully handled major client projects, developing custom scripts for System-Integration-Testing of web applications.} 
            \resumeItemHead{}{Made significant contributions to SimplifyQA, a product of Simplify3x, by creating custom methods for web automation.}
            \resumeItemHead{}{Mentored and trained interns on SimplifyQA, web automation testing, and Selenium.}
        \resumeItemListEnd

%----------- PROJECTS-----------------
\section {\href{https://github.com/bernardbdas} {\color{black} {PROJECTS}}}
    \resumeSubHeadingListStart
        
        \resumeItem 
            {\href{https://github.com/bernardbdas}
            {\color{black}
            {Predictive Customer Analytics:}}}
            {Contributed to a project focused on developing a predictive model that analyzed customer data to forecast customer behavior, including churn rate, purchasing patterns, and lifetime value. The primary objective was to assist businesses in optimizing marketing strategies, personalizing customer experiences, and improving customer retention.} 
        
        \resumeItem 
            {\href{https://github.com/bernardbdas}
            {\color{black}
            {Sentiment Analysis and Social Media Analytics:}}}
            {In this project, the objective was to develop a sentiment analysis model to analyze social media data and customer feedback. The end goal was to gain valuable insights into customer opinions, brand perception, and market trends. This information proved instrumental for reputation management, targeted marketing campaigns, and continuous product/service improvements.} 
        
        \resumeItem 
            {\href{https://github.com/bernardbdas}
            {\color{black}
            {Customer Segmentation and Targeting:}}}
            {I actively contributed to a customer segmentation and analysis project, employing clustering techniques and segmentation algorithms. The objective was to divide customers into distinct groups based on demographics, behavior, preferences, or purchasing habits. This segmentation approach provided valuable insights to businesses, enabling them to customize marketing campaigns, tailor product offerings, and optimize customer acquisition and retention strategies.} 
        
        \resumeItem 
            {\href{https://github.com/bernardbdas/bloomr-website}
            {\color{black}
            {Crop Recommendation WebApp using MEAN Stack:}}}
            {As part of my experience in web development, I successfully contributed to the development of a crop prediction web application using the MEAN Stack (MongoDB, Express.js, Angular, and Node.js). This application utilized a Flask API to integrate a multi-target regression model for predicting suitable crops based on real-time weather data fetched from a weather API.}
        
    \resumeSubHeadingListEnd

%-----------COURSES AND CERTIFICATIONS-----------------
\section{COURSES AND CERTIFICATIONS}
    \resumeSubHeadingListStart
        \resumeItem 
            {\href{https://www.udemy.com/certificate/UC-0671454d-5397-421d-8e13-2c2f348e05d7/}{\color{black} 
            {Machine Learning A-Z™: AI, Python & R + ChatGPT Bonus [2023]}}}
        
        \resumeItem 
            {\href{https://www.credly.com/badges/bdf2f146-b8c1-4cc0-b3df-81980f4df784/linked_in_profile}{\color{black} 
            {AWS Academy Graduate - AWS Academy Cloud Foundations}}}
        
        \resumeItem 
            {\href{https://www.udemy.com/certificate/UC-4c7ad5d4-de64-4e82-833b-5bc829bfec07}{\color{black} 
            {Python Programming 2021 Full Coverage: A Practical Approach}}}
    \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{EDUCATION}
    \resumeSubHeadingListStart
        \resumeSubheading
            {MCA, CHRIST (Deemed-to-be-University, Bengaluru)}
            {2021 - 2023}
            {with specialization in Data Analytics, CGPA: 69.67 \%}{}
            \vspace{5pt}
    
        \resumeSubheading
          {BSc. Computer Science (Hons.), St. Xavier's College, Kolkata}
          {2018 - 2021}
          {with specialization in Physics and Mathematics, CGPA: 72.40 \%}{}
          \vspace{5pt}
    
        \resumeSubheading
          {Senior Secondary, AUXILIUM CONVENT SCHOOL, BARASAT}
          {2016 - 2018}
          {with PCMB, GPA: 68.33 \%}{}
          \vspace{5pt}
     
        \resumeSubheading
          {Higher Secondary, AUXILIUM CONVENT SCHOOL, BARASAT}
          {2004 - 2016}
          {with Commercial Applications, GPA: 74.60 \%}{}
          \vspace{5pt}
    
    \resumeSubHeadingListEnd
    \vspace{-10pt}



%-----------Declaration------
%\section{Declaration}
%\begin{itemize}[leftmargin=0in, label={}]
% \small{\item{
% {I hereby declare that all the information reflected %above is true to the best of my belief.}\vspace{1pt}\\
% \hspace{360pt}{-Dishant Sharma}{} \\
% }}
% \end{itemize} 

%-------------------------------------------
\end{document}