\documentclass[../../bernard-resume-ats.tex]{subfiles}
\begin{document}

\section{Projects}
    \resumeSubHeadingListStart%
        \resumeProjectHeading{\titleItem{Cloud-Native CI/CD Platform} $|$ \emph{GitHub Actions, Kubernetes, Helm, ArgoCD, AWS}}{2025}
            \resumeItemListStart%
                \resumeItem{Designed and implemented a robust CI/CD platform using GitHub Actions, Helm, and ArgoCD for automated deployments to AWS EKS.}
                \resumeItem{Enabled blue-green deployments, automated rollbacks, and integrated monitoring for zero-downtime releases.}
            \resumeItemListEnd%
        \resumeProjectHeading{\titleItem{Infrastructure as Code Automation} $|$ \emph{Terraform, Ansible, AWS, Azure, GCP}}{2024}
            \resumeItemListStart%
                \resumeItem{Automated multi-cloud infrastructure provisioning and configuration management using Terraform and Ansible.}
                \resumeItem{Standardized environments across AWS, Azure, and GCP, reducing manual errors and deployment time by 70\%.}
            \resumeItemListEnd%
        \resumeProjectHeading{\titleItem{MLOps Pipeline for Model Lifecycle} $|$ \emph{Kubeflow, MLflow, Airflow, Docker, GCP}}{2024}
            \resumeItemListStart%
                \resumeItem{Built an end-to-end MLOps pipeline for model training, validation, deployment, and monitoring using Kubeflow, MLflow, and Airflow on GCP.}
                \resumeItem{Implemented automated retraining, model versioning, and canary deployments with Dockerized workflows.}
            \resumeItemListEnd%
        \resumeProjectHeading{\titleItem{Observability and Monitoring Stack} $|$ \emph{Prometheus, Grafana, ELK, Alertmanager}}{2023}
            \resumeItemListStart%
                \resumeItem{Deployed a centralized observability stack for microservices using Prometheus for metrics, Grafana for dashboards, and ELK for log aggregation.}
                \resumeItem{Configured Alertmanager for proactive incident response and integrated with Slack for real-time notifications.}
            \resumeItemListEnd%
        \resumeProjectHeading{\titleItem{Serverless Event-Driven Architecture} $|$ \emph{AWS Lambda, S3, DynamoDB, API Gateway}}{2023}
            \resumeItemListStart%
                \resumeItem{Developed a serverless event-driven system for data processing and notifications using AWS Lambda, S3, and DynamoDB.}
                \resumeItem{Exposed RESTful APIs via API Gateway and implemented monitoring with AWS CloudWatch.}
            \resumeItemListEnd%
        \resumeProjectHeading{\titleItem{Automated Security and Compliance} $|$ \emph{HashiCorp Vault, SonarQube, Trivy, Azure DevOps}}{2022}
            \resumeItemListStart%
                \resumeItem{Implemented automated security scanning and compliance checks in CI/CD pipelines using SonarQube and Trivy.}
                \resumeItem{Managed secrets and access control with HashiCorp Vault and integrated policy enforcement in Azure DevOps.}
            \resumeItemListEnd%
        \resumeProjectHeading{\titleItem{Cost-Optimized Multi-Cloud Deployment} $|$ \emph{Pulumi, Kubernetes, GCP, AWS, Azure}}{2022}
            \resumeItemListStart%
                \resumeItem{Orchestrated multi-cloud deployments using Pulumi and Kubernetes, optimizing resource allocation and cost across GCP, AWS, and Azure.}
                \resumeItem{Automated scaling and failover for high availability and business continuity.}
            \resumeItemListEnd%
    \resumeSubHeadingListEnd%

\end{document}