\documentclass[../../bernard-resume-ats.tex]{subfiles}
\begin{document}

\section{Projects}
    \resumeSubHeadingListStart%
        \resumeProjectHeading{\titleItem{SaaS Multi-Tenant Platform} $|$ \emph{Next.js, Node.js, AWS, Stripe, PostgreSQL}}{2025}
            \resumeItemListStart%
                \resumeItem{Architected and launched a scalable SaaS platform supporting multi-tenancy, subscription billing (Stripe), and role-based access control.}
                \resumeItem{Implemented SSR with Next.js, RESTful APIs with Node.js, and deployed on AWS ECS with CI/CD pipelines.}
            \resumeItemListEnd%
        \resumeProjectHeading{\titleItem{Real-Time Collaboration App} $|$ \emph{React, WebSockets, Firebase, Docker}}{2024}
            \resumeItemListStart%
                \resumeItem{Developed a Google Docs-style collaborative editor with real-time updates using React, WebSockets, and Firebase Realtime Database.}
                \resumeItem{Containerized the app with Docker for seamless deployment and scaling.}
            \resumeItemListEnd%
        \resumeProjectHeading{\titleItem{AI-Powered Content Generation Tool} $|$ \emph{OpenAI API, FastAPI, React, Vercel}}{2024}
            \resumeItemListStart%
                \resumeItem{Built a web app for automated blog and copywriting using OpenAI's GPT models, with a FastAPI backend and React frontend.}
                \resumeItem{Deployed globally on Vercel with serverless functions for low-latency inference.}
            \resumeItemListEnd%
        \resumeProjectHeading{\titleItem{E-Commerce Platform with Microservices} $|$ \emph{NestJS, GraphQL, MongoDB, Redis, Kubernetes}}{2023}
            \resumeItemListStart%
                \resumeItem{Engineered a microservices-based e-commerce platform with NestJS, GraphQL APIs, and MongoDB for product and order management.}
                \resumeItem{Used Redis for caching and Kubernetes for orchestration and scaling.}
            \resumeItemListEnd%
        \resumeProjectHeading{\titleItem{Progressive Web App for Task Management} $|$ \emph{Vue.js, PWA, Service Workers, GCP}}{2023}
            \resumeItemListStart%
                \resumeItem{Created a mobile-first PWA for task management with offline support using Vue.js and Service Workers.}
                \resumeItem{Deployed on Google Cloud Platform with automated CI/CD.}
            \resumeItemListEnd%
        \resumeProjectHeading{\titleItem{Serverless Event-Driven System} $|$ \emph{AWS Lambda, DynamoDB, S3, API Gateway}}{2022}
            \resumeItemListStart%
                \resumeItem{Designed a serverless backend for event processing and notifications using AWS Lambda, DynamoDB, and S3.}
                \resumeItem{Exposed RESTful endpoints via API Gateway and implemented monitoring with CloudWatch.}
            \resumeItemListEnd%
        \resumeProjectHeading{\titleItem{Secure Authentication \& Authorization System} $|$ \emph{OAuth2, JWT, Auth0, Express}}{2022}
            \resumeItemListStart%
                \resumeItem{Implemented a robust authentication and authorization system using OAuth2, JWT, and Auth0 for a multi-user web application.}
                \resumeItem{Integrated with Express.js middleware for secure API access and session management.}
            \resumeItemListEnd%
    \resumeSubHeadingListEnd%

\end{document}