%-------------------------
% Resume in Latex
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage{ifsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{xcolor}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\usepackage{tabularx}

% fontawesome
\usepackage{fontawesome5}
\input{glyphtounicode}
\pagestyle{fancy}
\fancyhf{}              % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]
    {\item\small
        {\textbf{#1}
        {: #2 \vspace{-2pt}}
    }
}

\newcommand{\resumeItemNonBold}[2]
    {\item\small
        {{#1}{: #2 \vspace{-2pt}}
    }
}

\newcommand{\resumeItemHead}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\resumeSubItemNoBold}[2]{\resumeItemNonBold{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{center}
    \textbf{\Large\scshape PRABHKIRAT KAUR} \\ \vspace{2pt}
    \small \faPhone* 7007110144 $|$ 
    \faEnvelope \hspace{2pt} \href{mailto:kiratsyal789@gmail.com}{\color{black} \underline {kiratsyal789@gmail.com}} $|$ 
    \faLinkedin \hspace{2pt}\href{www.linkedin.com/in/prabhkirat-kaur/} {\color{black} \underline{prabhkirat-kaur}} \hspace{1pt} $|$ 
    \address{\textifsymbol{18} Bengaluru,Karnataka}\\
\end{center}
\vspace{-15pt}

% --------PROGRAMMING SKILLS------------
\section{SKILLS}
\begin{itemize}[leftmargin=0in, label={}]
\vspace{2pt}
    \small{
    \item {
        \textbf{Languages} {: Python, R, SQL, Hive, Spark SQL.} \vspace{2pt} \\}
    \item {
        \textbf{Tools} {: GitHub, Jupyter-Notebook, Power Bi, Tableau, IBM Cognos, Anaplan, Alteryx, AWS.}\vspace{2pt} \\}
    \item {
        \textbf{Data Analysis Techniques} {: Classification, Regression, Clustering, Forecasting, Text and Social Media Analytics, Big Data Analytics.}\vspace{2pt} \\}
    }
\end{itemize} 

%-----------EXPERIENCE-----------------
\section{EXPERIENCE}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Bon-Heur Pharmaceuticals}{Haridwar, India}
    {Data Analyst Intern under Operations and Logistic division }{June 2022 - July 2022}
        \resumeItemListStart
        \vspace{-2pt}
            \resumeItemHead{}{Identified the tools and techniques for the required business analytics.} 
            \resumeItemHead{}{Performed the exploratory, univariate and multivariate data analysis process.} 
            \resumeItemHead{}{Performed various methods to understand and provide meaningful inferences from the Operational and Sales Data}
            \resumeItemHead{}{Developed suitable models for respective applications and visualisations for interpreting results.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd

%----------- PROJECTS-----------------
\section {\href{https://github.com/prabhkirat-kaur} {\color{black} {PROJECTS}}}
    \resumeSubHeadingListStart
        \resumeItem 
            {\href{https://github.com/prabhkirat-kaur}
            {\color{black}
            {Predictive Customer Analytics:}}}
            {Developed a predictive model that analyzes customer data to forecast customer behaviour, such as churn rate, purchasing patterns, and lifetime value. This can help businesses optimize marketing strategies, personalize customer experiences, and improve customer retention.} 
        \resumeItem 
            {{\color{black}
            {Sentiment Analysis and Social Media Analytics:}}}
            {Developed a sentiment analysis model that analyzes social media data and customer feedback to gain insights into customer opinions, brand perception, and market trends. This information can be used for reputation management, targeted marketing campaigns, and product/service improvements.} 
        \resumeItem 
            {{\color{black}
            {Customer Segmentation and Targeting:}}}
            {Applied clustering techniques and customer segmentation algorithms to divide customers into distinct groups based on demographics, behaviour, preferences, or purchasing habits. This segmentation can assist businesses in customizing marketing campaigns, tailoring product offerings, and optimizing customer acquisition and retention strategies.} 
        \resumeItem 
            {{\color{black}
            {A/B Testing and Conversion Rate Optimization:}}}
            {Implement rigorous A/B testing methodologies to analyze the impact of different website layouts, marketing messages, or product variations on conversion rates. By systematically testing and optimizing these elements, businesses can enhance their online presence, improve conversion rates, and drive higher sales.}
    \resumeSubHeadingListEnd
    \vspace{-10pt}

%-----------COURSES AND CERTIFICATIONS-----------------
\section{COURSES AND CERTIFICATIONS}
    \resumeSubHeadingListStart
        \resumeItem 
            {\href{https://courses.christ.skillsnetwork.site/certificates/1e1b5ec559404cf08102e8ef80ecf32d}{\color{black} 
            {Introduction to Big Data, Hadoop and the Ecosystems}}}

    \resumeSubHeadingListEnd
\vspace{-10pt}

%-----------EDUCATION-----------------
\section{EDUCATION}
    \resumeSubHeadingListStart
        \resumeSubheading
            {MBA, CHRIST (Deemed-to-be-University, Bengaluru)}{2021 - 2023}
            {with specialization in Business Analytics, CGPA: 58.74 \%}{}
            \vspace{5pt}
    
        \resumeSubheading
          {BCA, Shri Ramswaroop Memorial University, Uttar Pradesh}{2018 - 2021}
          {CGPA: 63.40 \%}{}
          \vspace{5pt}

        \resumeSubheading
          {Diploma in Computer Applications, Swami Vivekananda Subharti University, Meerut}{2019 - 2020}
          {CGPA: 63.36 \%}{}
          \vspace{5pt}
    
        \resumeSubheading
          {{\color{black} Sr. Secondary, SRIRAM SUBHASH CHAUDHARY INTER COLLEGE, CHAUSAR}}{2016 - 2018}
          {with PCM, GPA: 60 \%}{}
          \vspace{5pt}
     
        \resumeSubheading
          {Higher Secondary, SRIRAM SUBHASH CHAUDHARY INTER COLLEGE, CHAUSAR}{2014 - 2016}
          {GPA: 80.67 \%}{}
          \vspace{5pt}
     
        \resumeSubheading
          {Middle School, St Basil School, Basti}{2003 - 2013}
          {}{}
          \vspace{5pt}
    
    \resumeSubHeadingListEnd
    \vspace{-10pt}



%-----------Declaration------
%\section{Declaration}
%\begin{itemize}[leftmargin=0in, label={}]
% \small{\item{
% {I hereby declare that all the information reflected %above is true to the best of my belief.}\vspace{1pt}\\
% \hspace{360pt}{-Dishant Sharma}{} \\
% }}
% \end{itemize} 

%-------------------------------------------
\end{document}